Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-09-17 pres/acros.tex
Last paper changes and first presentation commit

@@

@@

\newacronym{CFD}{CFD}{Computational Fluid Dynamics}

@@

\newacronym{COMSOL}{COMSOL}{COMmon SOLution}

@@

\newacronym{DNP}{DNP}{delayed neutron precursor}

@@

@@

\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}

@@

\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}

@@

\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}

@@

\newacronym{MOSART}{MOSART}{Molten Salt Actinide Recycler and Transmuter}

@@

\newacronym{MPI}{MPI}{Message Passing Interface}
\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}

@@

\newacronym{NEAMS}{NEAMS}{Nuclear Energy Advanced Modeling and Simulation}

@@

\newacronym{NPP}{NPP}{Nuclear Power Plant}

@@

\newacronym{PDE}{PDE}{partial differential equation}

@@

\newacronym{PRIS}{PRIS}{Power Reactor Information System}

@@

\newacronym{REE}{REE}{rare earth element}

@@

\newacronym{ROD}{ROD}{Reactor Optimum Design}
\newacronym{SAMOFAR}{SAMOFAR}{Safety Assessment of the Molten Salt Fast Reactor}
\newacronym{SAM}{SAM}{System Analysis Module}

@@

\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}

@@

\newacronym{BOL}{BOL}{Beginning-of-Life}
\newacronym{ULOF}{ULOF}{Unprotected Loss of Flow}
\newacronym{LOSCA}{LOSCA}{Loss of Secondary Cooling Accident}

>>>>

\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}

@@

\newacronym{BOL}{BOL}{beginning of life}

@@

@@

@@

@@

\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
\newacronym{EOL}{EOL}{end of life}

@@

@@

@@

@@

@@

@@

\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}

@@

@@

@@

@@

@@

@@

@@
